Verifying Demonstrations

### 2020-04-22 paper/protocol-trusted.tex
No need for W subscript when P doesn't do anything
Updates protocol section title
Removes extra \\ in protocol figure
Updates proofshare figure

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The trusted-witnesses protocol}%
\label{trusted-witnesses-protocol}

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{protocol-overview-trusted}.
The goal of our protocol is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{fig:ProofFig}.
They are constructed through an interactive protocol between the protester and 
the witness, as depicted in \cref{protocol-overview-trusted} and described below.

\begin{figure}
  \centering
  \small
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
    protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

@@

In the terminology of \textcite{SelfCertifiedSybilFreePseudonyms}, the 
manifesto~\(\mfst\) is the context and it yields an identity domain.
A protester who wants to join the protest uses the manifesto~\(\mfst\) to
compute an identifier for the cause (the context) by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\)\footnote{%
  The result should be compared to that received from the organizer to check 
  that the \(\cid\) indeed is correct.
  This is to avoid that protesters use different \(\cid\)s for semantically 
  equivalent manifestos~\(\mfst\).
  However, we omit this in the protocol for readability.
}.
Afterwards, this is used to create the protester's protest-specific 
pseudonym~\(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.

@@

In the participation phase, the protester and 
the witness construct the proof share of the protester (\cref{fig:ProofFig}).

@@

To achieve this, the witness computes \iac{NIZK} proof~\(\corr_{\wid}\), 
proving the correctness of \(\wid\) while also signing the time~\(t\) and 
location~\(l\).
More specifically, we have that
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\sskw}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t, l).
\end{multline*}
Finally, the complete proof share is the tuple \[
  \psh_W = (\cid, \pid, \wid, t, l, \corr_{\wid}).
\]

@@

\begin{figure*}
  \centering
  \small
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid]
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      %W\to P\colon & (\wid, t, l)
    \end{align*}
    \caption{Join and participation}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      W\colon & \TSsubmit[(\cid, \pid, \wid, t, l, \corr_{\wid})],\quad 
      \text{where} \\
        & \corr_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' =
              \ACblind[\ACsign[_{\sskw}][\sk_W]]\mright\} \\
        & \qquad\qquad (\cid, \pid, \wid, t, l)
    \end{align*}
    \caption{Submission}
  \end{subfigure}
  \caption{%
    An overview of the protocol with trusted witnesses.
    The organizer~\(O\) broadcasts the manifesto.
    The protester~\(P\) with pseudonym~\(\pid\) in the context of the protest 
    (\(\cid\)),
    the witness~\(W\) with pseudonym~\(\wid\) in the context of that protester 
    and
    their computations are as in \cref{fig:ProofFig}.
    Finally, \(W\) submits the proof share to a public ledger~\(\TS\) for 
    permanent storage.
  }%
  \label{protocol-overview-trusted}
\end{figure*}
%\normalsize

>>>>

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{Crowd counting with trusted witnesses}%
\label{trusted-witnesses-protocol}

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{protocol-overview-trusted}.
The goal of our protocol is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{proofshare-trusted-fig}.
They are constructed through an interactive protocol between the protester and 
the witness, as depicted in \cref{protocol-overview-trusted} and described below.

\begin{figure}
  \centering
  \small
  \includegraphics{proofshare-trusted.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester~\(P\)'s protest-specific pseudonym~\(\pid\) is computed using 
    the protester's key~\(\sk_P\) and \(\cid\).
    The witness \(W\)'s \emph{protester}-specific identifier \(\wid\) is 
    computed using the witness's key~\(\sk_W\) and the protester's 
    pseudonym~\(\pid\).
    \(t\) is the time (interval) and \(l\) is the location (area) as determined 
    by the trusted witness~\(W\).
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
    = \dotsb][\cid, \pid, \wid, t, l]\)) while also proving the correctness of 
    \(\wid\) and knowledge of a signature on \(\sk_W\) by some \ac{CA}.
  }%
  \label{proofshare-trusted-fig}
\end{figure}%

@@

In the terminology of \textcite{SelfCertifiedSybilFreePseudonyms}, the 
manifesto~\(\mfst\) is the context and it yields an identity domain.
A protester who wants to join the protest uses the manifesto~\(\mfst\) to
compute an identifier for the cause (the context) by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\)\footnote{%
  The result should be compared to that received from the organizer to check 
  that the \(\cid\) indeed is correct.
  This is to avoid that protesters use different \(\cid\)s for semantically 
  equivalent manifestos~\(\mfst\).
  However, we omit this in the protocol for readability.
}.
Afterwards, this is used to create the protester's protest-specific 
pseudonym~\(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{proofshare-trusted-fig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.

@@

In the participation phase, the protester and 
the witness construct the proof share of the protester (\cref{proofshare-trusted-fig}).

@@

To achieve this, the witness computes \iac{NIZK} proof~\(\corr_{\wid}\), 
proving the correctness of \(\wid\) while also signing the time~\(t\) and 
location~\(l\).
More specifically, we have that
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\sskw}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t, l).
\end{multline*}
Finally, the complete proof share is the tuple \[
  \psh = (\cid, \pid, \wid, t, l, \corr_{\wid}).
\]

@@

\begin{figure*}
  \centering
  \small
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid]
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid]% \\
      %W\to P\colon & (\wid, t, l)
    \end{align*}
    \caption{Join and participation}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      W\colon & \TSsubmit[(\cid, \pid, \wid, t, l, \corr_{\wid})],\quad 
      \text{where} \\
        & \corr_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' =
              \ACblind[\ACsign[_{\sskw}][\sk_W]]\mright\} \\
        & \qquad\qquad (\cid, \pid, \wid, t, l)
    \end{align*}
    \caption{Submission}
  \end{subfigure}
  \caption{%
    An overview of the protocol with trusted witnesses.
    The organizer~\(O\) broadcasts the manifesto.
    The protester~\(P\) with pseudonym~\(\pid\) in the context of the protest 
    (\(\cid\)),
    the witness~\(W\) with pseudonym~\(\wid\) in the context of that protester 
    and
    their computations are as in \cref{proofshare-trusted-fig}.
    Finally, \(W\) submits the proof share to a public ledger~\(\TS\) for 
    permanent storage.
  }%
  \label{protocol-overview-trusted}
\end{figure*}
%\normalsize
